Paradigms in Physics 2.0

### 2017-06-27 paper.tex
polish process text a tad

\subsection{Background}
The Paradigms in Physics project began in 1996, when three faculty
members at Oregon State applied to the NSF for funding to redesign the
upper-division curriculum.  The motivation for the original Paradigms
project was in fact similar to the motivation for Paradigms 2.0: a
desire to soften the ``brick wall'' encountered by students upon
reaching the junior year, within the constraint that transfer students
must be able to graduate with two years of upper-division
courses~\cite{manogue2001paradigms}.  The process of redesigning the
curriculum was dominated by the creation index cards listing subject
content, and sorting these cards into courses.  This process involved
the entire faculty, and culminated in a unanimous agreement to adopt
the resulting curriculum.

@@

The committee met for ??? weeks to discuss existing challenges and
sort the cards into new stacks corresponding to new and reordered
courses.  When we discussed major changes to a course, we often
invited interested faculty to join us to provide their own perspective
on possible challenges and improvements.  Once we had a draft
proposal, we began inviting each faculty member in to see the cards
and discuss the proposed sequence of courses.  In addition, we had a
meeting with all the current students to explain the proposed changes
and request feedback.

When we had obtained feedback from the entire faculty, we scheduled
\emph{two} faculty meetings (DURATION?).  In the first meeting, we
presented our proposal in detail.  This was needed for several
reasons.  Those faculty we met with first may not have seen the final
proposal.  Some faculty during their individual meetings chose to
focus on a small subset of the curriculum, often relating to courses
they had themselves taught.  In one meeting we presented the proposal
and fielded questions.  In a second faculty meeting, we again
presented our proposal, and opened the floor for discussion.  After
considerable discussion, we unanimously voted to adopt the proposed
changes.

>>>>

\subsection{Background}
The Paradigms in Physics project began in 1996, when three faculty
members at Oregon State applied to the NSF for funding to redesign the
upper-division curriculum.  The motivation for the original Paradigms
project was in fact similar to the motivation for Paradigms 2.0: a
desire to soften the ``brick wall'' encountered by students upon
reaching the junior year, within the constraint that transfer students
must be able to graduate with two years of upper-division
courses~\cite{manogue2001paradigms}.  On top of this, there was a
desire to provide students with a broad knowledge of physics prior to
the GRE exams in the fall of their senior year.  The process of
redesigning the curriculum was dominated by the creation index cards
listing subject content, and sorting these cards into courses.  This
process involved the entire faculty, and culminated in a unanimous
agreement to adopt the resulting curriculum.

@@

The committee met twice a week to discuss existing challenges and sort
the cards into new stacks corresponding to new and reordered courses.
When we discussed major changes to a course, we often invited
interested faculty to join us to provide their own perspective on
possible challenges and improvements.  Once we had a draft proposal,
we began inviting each faculty member in to see the cards and discuss
the proposed sequence of courses.  In addition, we had a meeting with
all the current students to explain the proposed changes and request
feedback.

When we had obtained feedback from the entire faculty, we scheduled
\emph{two} full faculty meetings.  In the first meeting, we presented
our proposal in detail and invited questions, but not discussion.
This was needed for several reasons.  Those faculty we met with first
may not have seen the final proposal.  Some faculty during their
individual meetings chose to focus on a small subset of the
curriculum, often relating to courses they had themselves taught.  In
one meeting we presented the proposal and fielded questions.  In a
second faculty meeting, we again presented our proposal, and opened
the floor for discussion.  After considerable discussion, we
unanimously voted to adopt the proposed changes.
